%!TEX root = ../Airbnb_CaseStudy.tex
\section{Questionary}
\label{sec:Questionary}
Not all the desired information can be caught by Web Logs, Web Beacons, JavaScript Tags and Packet Sniffing. There are clickstream holes, that can be easily filled by a methods like questionaries. For example: Website analysts try to find out how someone became aware of a website, but browser settings, wrong redirects or something weird in the links to the website prevents to obtain the referring URL. In this case, a surveys can help find answers to this questions. \citep[p. 64]{Kaushik07} It is important to know the advantages and disadvantages of website and post-visit questionaries. Website surveys are more effective in retrieving thoughts, that are given during the visit. Post-visit surveys are more effective in getting information of an experience, that happened after a website visit.
\vspace{0.2cm}

Invitations to post-visit questionaries are usually send out via email to the customer after a certain amount of time has passed after the transaction or visit on the web site. On the other hand website questionaries are offered to the user of a web site at the time he is actually interacting with the site. \citep[p. 65-66]{Kaushik07} We need both kind of questionaries to paint a complete picture. On the one hand to get ratings about the usability and onsite experience, on the other hand to retrieve information about the stay in the accomodation.

\subsection{Website Questionary}
\label{sec:Website_Questionary}

Not every visitor uses all the available features of Airbnb. We do not want to ask questions, that the user cannot answer. Therefore we will track which pages the user visited and only show questions about subjects, that he can know about.\\

\textbf{After the booking process}

\vspace{0.2cm}

Do you agree that comments from other people influenced your decision?
\newline
Strongly disagree | 1 2 3 4 5 | Strongly agree \\

Do you agree that rating of the place influenced your decision?
\newline
Strongly disagree | 1 2 3 4 5 | Strongly agree \\

Do you agree that photos influenced your decision?
\newline
Strongly disagree | 1 2 3 4 5 | Strongly agree \\

Do you agree that to find an appropriate place was easy?
\newline
Strongly disagree | 1 2 3 4 5 | Strongly agree \\

\textit{Ask this question only if we tracked the visitor used neighbourhoods} \\
Rate your experience of neighbourhoods:
\newline
Very Bad | 1 2 3 4 5 | Very good \\

Did you have any problems during booking?
\begin{itemize}
	\item No, booking was easy.
    \item Yes, \underline{\hspace{8cm}}
\end{itemize}
\vspace{0.2cm}

Rate the overall impression of the Airbnb service?
\begin{itemize}
 \item Everything was fine.
 \item I had few difficulties. I'll explain in the comments.
 \item Experience is bad, my remarks are in the comments.
 \item Comments: \underline{\hspace{8cm}}
\end{itemize}

\subsection{Post-visit Questionary}
\label{sec:Post-visit_Questionary}

We use open questions in order to make qualitative analysis and find out problems which we were not expecting.
\par
\vspace{0.2cm}

\textbf{After the stay in an accomodation}
\vspace{0.2cm}

Did you have any problems getting to the place?
\begin{itemize}
	\item No, it was easy.
    \item Yes, \underline{\hspace{8cm}}
\end{itemize}
\vspace{0.2cm}

Were there any inconsistencies between the place and it`s description?
\begin{itemize}
	\item No, the description is accurate.
    \item Yes, \underline{\hspace{8cm}}
\end{itemize}
\vspace{0.2cm}

Were there any inconsistencies between the place and comments on page?
\begin{itemize}
	\item No, comments are accurate.
    \item Yes, \underline{\hspace{8cm}}
\end{itemize}
\vspace{0.2cm}

Was the process of negotiation with host comfortable for you?
\begin{itemize}
 \item Everything was fine, I had no problems.
 \item I had few difficulties. I'll explain in the comments.
 \item My Experience was bad, I'll tell you in the comments.
 \item It was a disaster! I'll tell you in the comments.
 \item Comments: \underline{\hspace{8cm}}
\end{itemize}
\vspace{0.2cm}

Did you have any problems while staying?
\begin{itemize}
	\item No, it was great.
    \item Yes, \underline{\hspace{8cm}}
\end{itemize}
